dendro

### 2017-09-06 analysis/analysis_chronologies.Rmd
update anlaysis chrono and parser climate data
update and get crono by site

```{r, echo=FALSE}
machine <- 'ajpelu'
#machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

cro_b <- cro_sjb %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('biweight')) %>% 
  select(bai_mean = SJstd, samp.depth, year, treatment)

cro_notb <- cro_sjnotb %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('No biweight')) %>% 
  select(bai_mean = SJstd, samp.depth, year, treatment)

@@

cro_cab_h_aux <- cro_cab_h %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('biweight')) %>% 
  select(bai_mean = CAstd, samp.depth, year, treatment)

cro_canotb_h_aux <- cro_canotb_h  %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('No biweight')) %>% 
  select(bai_mean = CAstd, samp.depth, year, treatment)

@@

cro_cab_l_aux <- cro_cab_l %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('biweight')) %>% 
  select(bai_mean = CAstd, samp.depth, year, treatment)

cro_canotb_l_aux <- cro_canotb_l  %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('No biweight')) %>% 
  select(bai_mean = CAstd, samp.depth, year, treatment)

@@

>>>>

```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

cro_b <- cro_sjb %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('biweight')) %>% 
  dplyr::select(bai_mean = SJstd, samp.depth, year, treatment)

cro_notb <- cro_sjnotb %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('No biweight')) %>% 
  dplyr::select(bai_mean = SJstd, samp.depth, year, treatment)

@@

cro_cab_h_aux <- cro_cab_h %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('biweight')) %>% 
  dplyr::select(bai_mean = CAstd, samp.depth, year, treatment)

cro_canotb_h_aux <- cro_canotb_h  %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('No biweight')) %>% 
  dplyr::select(bai_mean = CAstd, samp.depth, year, treatment)

@@

cro_cab_l_aux <- cro_cab_l %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('biweight')) %>% 
  dplyr::select(bai_mean = CAstd, samp.depth, year, treatment)

cro_canotb_l_aux <- cro_canotb_l  %>% 
  mutate(year = as.numeric(rownames(.))) %>% 
  mutate(treatment = as.factor('No biweight')) %>% 
  dplyr::select(bai_mean = CAstd, samp.depth, year, treatment)

@@

## Export data of bai (chro)
write.csv(cro_sites, file=paste(di, "data/cronos_medias/cronos_sites.csv", sep=""), row.names = FALSE)
